Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-07 WSSSPE2_report/WSSSPE2_review.tex
Section 1. Outline modified.

This report extends a previous report that discussed the submission,
peer-review, and peer-grouping processes in detail~\cite{WSSSPE2-pre-report}.
It is also based on a collaborative set of notes taken through a google doc
during the workshop~\cite{WSSSPE2-google-notes}. Overall, the report discusses
the organization work done before the workshop (\S\ref{sec:preworkshop}); the
keynotes (\S\ref{sec:keynotes}); a series of lightning talks (\S\ref{sec:lightning}),
intended to give an opportunity for attendees to quickly highlight an important issue
or a potential solution; a session on defining sustainability
(\S\ref{sec:defining}); five breakout sessions that explored sustainability
(\S\ref{sec:exploring}); software development experiences (\S\ref{sec:devel});
credit \& incentives (\S\ref{sec:credit}); reproducibility, reuse, \& sharing
(\S\ref{sec:reproduce}); code testing \& code review
(\S\ref{sec:code_testing}); and some conclusions (\S\ref{sec:conclusions}). The
report also includes an incomplete list of attendees (Appendix~\ref{sec:attendees}).

@@

\note{
Lighting talks, breakout groups, working groups are all different. Lightning
talks were new in WSSSPE2. They were offered to all paper contributors, and some
other attendees, those who got travel awards. Breakout groups in WSSSPE1 were
just discussions about topics; in WSSSPE2, the breakout groups were supposed to
come up with plans for actions in specific areas. The idea of working groups is
that they will come out of breakout groups as a way for the groups to actually
do the actions over time, not at the workshops.
}

>>>>

This report extends a previous report that discussed the submission,
peer-review, and peer-grouping processes in detail~\cite{WSSSPE2-pre-report}.
It is also based on a collaborative set of notes taken through a google doc
during the workshop~\cite{WSSSPE2-google-notes}. Overall, the report discusses
the organization work done before the workshop (\S\ref{sec:preworkshop}); the
keynotes (\S\ref{sec:keynotes}); a series of lightning talks
(\S\ref{sec:lightning}), intended to give an opportunity for attendees to
quickly highlight an important issue or a potential solution; a session on
defining sustainability (\S\ref{sec:defining}). The report also gives summaries
of action plans proposed by five breakout sessions, which explored in specific
areas including sustainability (\S\ref{sec:exploring}); software development
experiences (\S\ref{sec:devel}); credit \& incentives (\S\ref{sec:credit});
reproducibility, reuse, \& sharing (\S\ref{sec:reproduce}); code testing \& code
review (\S\ref{sec:code_testing}). Lastly, the report also includes some
conclusions (\S\ref{sec:conclusions}) and an incomplete list of attendees
(Appendix~\ref{sec:attendees}).

@@

\begin{comment}
Lighting talks, breakout groups, working groups are all different. Lightning
talks were new in WSSSPE2. They were offered to all paper contributors, and some
other attendees, those who got travel awards. Breakout groups in WSSSPE1 were
just discussions about topics; in WSSSPE2, the breakout groups were supposed to
come up with plans for actions in specific areas. The idea of working groups is
that they will come out of breakout groups as a way for the groups to actually
do the actions over time, not at the workshops.
\end{comment{
